---
title: "Statistics for Data Science Project 2021/2022 - Risk of Business Failure"
subtitle: "Data Understanding & Preprocessing"
output: 
  html_notebook:
    toc: true
    theme:
      bootswatch: cerulean   
---
By:  
Carla Lorena Trejo Silva\
Jordanos Feyissa Gemechu\
Bruno Javier Limon Avila\

```{r}
library(ggplot2)
library(skimr)
library(forcats)
library(moments)
```
```{r}
# cleaning the environment
rm(list=ls())
# loading the dataset
load(file="aida.RData")
# loading functions to be used
source("functions.R")
```
# 1.0 Data Understanding & Preprocessing
***
Taking a look at the features within our dataset, searching for NA and anomalies, while also making the necessary changes in order to perform further analysis.

## 1.1 Data Understanding
***
Summary of dataset divided by type of variable. Includes information like number of missing and unique values, as well as mean and percentiles for the numerical variables
```{r}
skim(aida)
```  
```{r}
# first rows of the dataset
head(aida)
```
```{r}
# a first in-depth look at some of the features, particularly those that stand out from the others, which repeat themselves for current and previous 2 years. Here we take a look at their unique values and their frequency
table(aida$`Incorporation year`)
table(aida$`Last accounting closing date`)
table(aida$`Legal status`)
table(aida$`Legal form`)
table(aida$`Registered office address - Region`)
```
## 1.2 Data Preprocessing
***
### 1.2.1 Creation of new variables
***
features added by using the functions in "functions.R"
- size is obtained with the log(aida$Total assetsth EURLast avail. yr)
- age is equal to the difference between last accounting closing date and incorporation year
- status is considered active for every legal status != active
```{r}
aida <- getSize(aida)
aida <- getGeoArea(aida)
aida <- getStatus(aida)
aida <- getAge(aida)
aida <- getATECO(aida)
aida <- getLiquidity(aida)
```
```{r}
# separating dataset filtering by historical data
aida.currYr <- getCurrYr(aida)
aida.yr1 <- getYr1(aida)
aida.yr2 <- getYr2(aida)
```
```{r}
# further dividing the dataset, this time by year of last accounting date
aida2017 <- aida.currYr[aida.currYr$`Last accounting closing date` == 2017,]
aida2018 <- aida.currYr[aida.currYr$`Last accounting closing date` == 2018,]
aida2019 <- aida.currYr[aida.currYr$`Last accounting closing date` == 2019,]
```
```{r}
actyear <- c('2017','2017','2018','2018','2019','2019')
actstatus <- c('Active','Failed','Active','Failed','Active','Failed')
actFrequency <- c(table(aida2017$Status),table(aida2018$Status),table(aida2019$Status))
ActiveFailedTable <- data.frame(Year=actyear, Status=actstatus, Frequency=actFrequency)
knitr::kable(ActiveFailedTable, caption = 'Frequency of Active and Failed companies in the last 3 years')

rm(actyear, actstatus, actFrequency, ActiveFailedTable)
```
```{r}
knitr::kable(table(aida$GeoArea), caption = 'Frequency of companies based on Geographical Location')
```
## 1.3 Data Visualization
***
```{r}
# number of companies by legal status plot
ggplot(data=aida, aes(x=fct_infreq(`Legal status`), fill=`Legal status`)) +
  geom_bar() +
  coord_flip() +
  theme_bw() +
  theme(legend.key=element_blank(), legend.key.size=unit(13,"point")) + 
  ggtitle("Number of companies by legal status")
```
```{r}
# number of companies by legal form plot
ggplot(data=aida, aes(x=fct_infreq(`Legal form`), fill=`Status`)) +
  geom_bar() +
  coord_flip() +
  theme_bw() +
  theme(legend.key=element_blank(), legend.key.size=unit(13,"point")) +
  ggtitle("Number of companies by legal form")
```
```{r}
# number of companies by region plot
ggplot(data=aida, aes(x=fct_infreq(`Registered office address - Region`), fill=`Status`)) +
  geom_bar() +
  coord_flip() +
  theme_bw() +
  theme(legend.key=element_blank(), legend.key.size=unit(13,"point")) +
  ggtitle("Number of companies by region")
```
```{r}
ggplot(data=aida, aes(x=ATECO.Sector.Name, fill=Status)) +
  geom_bar() +
  theme_bw() +
  coord_flip() +
  theme(legend.key=element_blank(), legend.key.size=unit(13,"point")) +
  ggtitle("Number of companies of each ATECO sector divided by Active/Failed")
```
```{r}
# number of companies by geographic area plot
ggplot(data=aida, aes(x=`GeoArea`, fill=`GeoArea`)) +
  geom_bar() +
  coord_flip() +
  theme_bw() +
  theme(legend.key=element_blank(), legend.key.size=unit(13,"point")) +
  ggtitle("Number of companies by geographic area")
```
```{r}
# number of companies by size plot
ggplot(data=aida, aes(x=`Status`, fill=`Status`)) +
  geom_bar() +
  theme_bw() +
  coord_flip() +
  theme(legend.key=element_blank(), legend.key.size=unit(13,"point")) +
  ggtitle("Number of active and failed companies")
```
```{r}
# distribution of age plot
ggplot(data=aida, aes(x=`Age`, fill=`Age`)) +
  geom_histogram(aes(y = ..density..), binwidth=2, colour = 1, fill = "white") +
  geom_density(lwd = 1, colour = 4) +
  geom_vline(xintercept = mean(aida$Age), col = "red", lwd = .8, lty = 2) +
  theme_bw() + 
  ggtitle("Company frequency distribution of age")
```
```{r}
# density of size(Total assets) plot
h <- hist(aida$Size, breaks = "FD", plot = FALSE)
ggplot(data=aida, aes(x=`Size`, fill=`Size`)) +
  geom_histogram(aes(y = ..density..), breaks = h$breaks, colour = "gray", fill = "white") +
  geom_density(lwd = 1, colour = 4) +
  geom_vline(xintercept = mean(aida$Size), col = "red", lwd = .8, lty = 2) +
  theme_bw() + 
  ggtitle("Company frequency distribution of Size")
```
```{r}
# density of Liquidity plot
h <- hist(aida$LiquidityRatio, breaks = "FD", plot = FALSE)
ggplot(data=aida, aes(x=`LiquidityRatio`, fill=`LiquidityRatio`)) +
  geom_histogram(aes(y = ..density..), breaks = h$breaks, colour = "gray", fill = "white") +
  geom_density(lwd = 1, colour = 4) +
  geom_vline(xintercept = mean(aida$LiquidityRatio), col = "red", lwd = .8, lty = 2) +
  theme_bw() +  
  ggtitle("Company frequency distribution of Liquidity")
```
Analyzing skewness and kurtosis of some variables
```{r}
skewness(aida$Age)
kurtosis(aida$Age)

skewness(aida$Size)
kurtosis(aida$Size)

skewness(aida$LiquidityRatio)
kurtosis(aida$LiquidityRatio)
```

```{r}
# Boxplot age and region
ggplot( data=aida, aes(x=Age, GeoArea)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Age and Geographical Region boxplot")
```
## 1.4 Anomaly Detection
***
```{r}
# Boxplot age
ggplot( data=aida, aes(x=Age)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Age boxplot")
```
```{r}
iqr <- IQR(aida$Age)
q1 <- quantile(aida$Age,0.10)
q3 <- quantile(aida$Age,0.90)
lower.whisker <- q1 - 1.5*iqr
upper.whisker <- q3 + 1.5*iqr 

min(aida$Age)
max(aida$Age)
mean(aida$Age)
q1
q3
```
```{r, fig.width=9, fig.height=4}
# Boxplot Age and Legal form
ggplot( data=aida, aes(x=Age, `Legal form`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Age and Legal form")
```

```{r, fig.width=9, fig.height=4}
# Boxplot Age and ATECO sector
ggplot( data=aida, aes(x=Age, `ATECO.Sector.Name`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Age and ATECO sector")
```
```{r, fig.width=9, fig.height=4}
# Boxplot Age and Region
ggplot( data=aida, aes(x=Age, `Registered office address - Region`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Age and Region boxplot")
```
```{r}
# Boxplot Size before log(Total assets)
ggplot( data=aida,aes(x=`Total assetsth EURLast avail. yr`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Total assetsth EURLast avail. yr boxplot")
```
```{r}
# Boxplot Size (Total assets)
ggplot( data=aida,aes(x=Size)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Size boxplot")
```
```{r}
iqr <- IQR(aida$Size)
q1 <- quantile(aida$Size,0.10)
q3 <- quantile(aida$Size,0.90)
lower.whisker <- q1 - 1.5*iqr
upper.whisker <- q3 + 1.5*iqr 

min(aida$Size)
max(aida$Size)
mean(aida$Size)
q1
q3
```
```{r, fig.width=9, fig.height=4}
# Boxplot size and Legal form
ggplot( data=aida, aes(x=Size, `Legal form`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Size and Legal form")
```

```{r, fig.width=9, fig.height=4}
# Boxplot size and ATECO sector
ggplot( data=aida, aes(x=Size, `ATECO.Sector.Name`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Size and ATECO sector")
```
```{r, fig.width=9, fig.height=4}
# Boxplot age and Region
ggplot( data=aida, aes(x=Size, `Registered office address - Region`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Size and Region boxplot")
```

```{r}
# Boxplot Liquidity
ggplot( aida, aes(x=LiquidityRatio)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Liquidity Boxplot")
```
```{r}
iqr <- IQR(aida$LiquidityRatio)
q1 <- quantile(aida$LiquidityRatio,0.10)
q3 <- quantile(aida$LiquidityRatio,0.90)
lower.whisker <- q1 - 1.5*iqr
upper.whisker <- q3 + 1.5*iqr 

min(aida$LiquidityRatio)
max(aida$LiquidityRatio)
mean(aida$LiquidityRatio)
q1
q3
```
```{r, fig.width=9, fig.height=4}
# Boxplot size and Legal form
ggplot( data=aida, aes(x=LiquidityRatio, `Legal form`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("LiquidityRatio and Legal form")
```
```{r, fig.width=9, fig.height=4}
# Boxplot size and ATECO sector
ggplot( data=aida, aes(x=LiquidityRatio, `ATECO.Sector.Name`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("LiquidityRatio and ATECO sector")
```
```{r, fig.width=9, fig.height=4}
# Boxplot age and Region
ggplot( data=aida, aes(x=LiquidityRatio, `Registered office address - Region`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("LiquidityRatio and Region boxplot")
```
```{r}
# Boxplot cash flow (Total assets)
ggplot( data=aida,aes(x=`Cash Flowth EURLast avail. yr`)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Cash Flow boxplot")
```
