---
title: "Statistics for Data Science Project 2021/2022 - Risk of Business Failure"
subtitle: "Question A"
output: 
  html_notebook:
    toc: true
    theme:
      bootswatch: cerulean 
---
# Data Preparation
***
We load the necessary libraries as well as the aida dataset itself, along with any needed variable obtained during the first section.

```{r}
library(ggplot2)
library(dplyr) 
```
```{r}
# cleaning the environment
rm(list=ls())
# loading the dataset
load(file="aida.RData")
# loading functions to be used
source("functions.R")
```
```{r}
# features added by using the functions in "functions.R"
aida <- getSize(aida)
aida <- getGeoArea(aida)
aida <- getStatus(aida) 
aida <- getAge(aida)
aida <- getATECO(aida)
aida <- getLiquidity(aida)
# separating dataset filtering by year
aida.currYr <- getCurrYr(aida)
aida.yr1 <- getYr1(aida)
aida.yr2 <- getYr2(aida)
# focusing on a specific year
aida2018 <- aida.currYr[aida.currYr$`Last accounting closing date` == 2018,]
```
# 2.0 Question A
***
Compare the distributions of size/age/other between failed and active companies at a specific year?

- do they change for a specific company form (SPA, SRL, etc.)
- do they change for a specific industry sector? (see ATECO sectors)

## 2.1 Age Distribution
***
Let us look at the density function of the _Age_ feature we obtained before at certain years, namely 2018, since that is the year where we have the biggest amount of information available.

```{r, fig.width=10, fig.height=3}
# density of age in 2018
ggplot(data=aida2018, aes(x=Age, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of company ages in 2018")
```
```{r}
# data for statistical tests, age distribution in 2018
aida2018.ActiveAge <- aida2018[aida2018$Status=='Active','Age']
aida2018.FailedAge <- aida2018[aida2018$Status=='Failed','Age']

wilcox.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'two.sided')
wilcox.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'less')
wilcox.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'greater')

t.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'two.sided')
t.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'less')
t.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'greater')

ks.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'two.sided')
ks.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'less')
ks.test(aida2018.ActiveAge, aida2018.FailedAge, alternative = 'greater')

rm(aida2018.ActiveAge, aida2018.FailedAge)
```

### 2.1.1 Age Distribution for specific company forms
***
In order to select a company form that would provide us with a statistically significant difference, we decided to take a look at figure X to see how _Legal form_ interacts with _Age_. 
By looking at the previous figure and the plots in section 1.3., we decided to focus on S.P.A. companies because they are on average the oldest, and also on S.R.L., being the most frequent.

<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of age in 2018 for S.R.L. and S.P.A. companies
ggplot(data=aida2018[aida2018$`Legal form` == 'S.R.L.',], aes(x=`Age`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of age for S.R.L. companies in 2018")
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of age in 2018 for S.P.A. companies
ggplot(data=aida2018[aida2018$`Legal form` == 'S.P.A.',], aes(x=`Age`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of age for S.P.A. companies in 2018")
```
</div>
</div>
```{r}
# data for statistical tests, age distribution for specific legal form
aida2018.ActiveAgeSRL <- aida2018[aida2018$Status=='Active' & aida2018$`Legal form` == 'S.R.L.' ,'Age']
aida2018.FailedAgeSRL <- aida2018[aida2018$Status=='Failed' & aida2018$`Legal form` == 'S.R.L.' ,'Age']
aida2018.ActiveAgeSPA <- aida2018[aida2018$Status=='Active' & aida2018$`Legal form` == 'S.P.A.' ,'Age']
aida2018.FailedAgeSPA <- aida2018[aida2018$Status=='Failed' & aida2018$`Legal form` == 'S.P.A.' ,'Age']

t.test(aida2018.ActiveAgeSRL, aida2018.FailedAgeSRL, alternative = 'two.sided')
t.test(aida2018.ActiveAgeSRL, aida2018.FailedAgeSRL, alternative = 'less')
t.test(aida2018.ActiveAgeSRL, aida2018.FailedAgeSRL, alternative = 'greater')

t.test(aida2018.ActiveAgeSPA, aida2018.FailedAgeSPA, alternative = 'two.sided')
t.test(aida2018.ActiveAgeSPA, aida2018.FailedAgeSPA, alternative = 'less')
t.test(aida2018.ActiveAgeSPA, aida2018.FailedAgeSPA, alternative = 'greater')

rm(aida2018.ActiveAgeSRL, aida2018.FailedAgeSRL, aida2018.ActiveAgeSPA, aida2018.FailedAgeSPA)
```

### 2.1.2 Age Distribution for specific ATECO sectors
***
As before with _Legal form_, we inspect the boxplots in figure X of _Age_ and _ATECTO Sector Codes_ in search of interesting insights.

In a similar fashion, we picked the most frequent sector, being G, and the oldest on average, B, but with further inspection realized that B has a frequency of only 3001 records, representing less than 0.2% of the dataset, we therefore went with a more representative sector, L, with 205858 observations.

<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of age in 2018 for ATECO G companies
ggplot(data=aida2018[aida2018$ATECO.Sector.Name == 'G',], aes(x=`Age`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of age for ATECO G companies in 2018")
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of age in 2018 for ATECO L companies
ggplot(data=aida2018[aida2018$ATECO.Sector.Name == 'L',], aes(x=`Age`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of age for ATECO L companies in 2018")
```
</div>
</div>

```{r}
# data for statistical tests, age distribution for specific ATECO sector
aida2018.ActiveAgeG <- aida2018[aida2018$Status=='Active' & aida2018$ATECO.Sector.Name == 'G' ,'Age']
aida2018.FailedAgeG <- aida2018[aida2018$Status=='Failed' & aida2018$ATECO.Sector.Name == 'G' ,'Age']
aida2018.ActiveAgeL <- aida2018[aida2018$Status=='Active' & aida2018$ATECO.Sector.Name == 'L' ,'Age']
aida2018.FailedAgeL <- aida2018[aida2018$Status=='Failed' & aida2018$ATECO.Sector.Name == 'L' ,'Age']

t.test(aida2018.ActiveAgeG, aida2018.FailedAgeG, alternative = 'two.sided')
t.test(aida2018.ActiveAgeG, aida2018.FailedAgeG, alternative = 'less')
t.test(aida2018.ActiveAgeG, aida2018.FailedAgeG, alternative = 'greater')

t.test(aida2018.ActiveAgeL, aida2018.FailedAgeL, alternative = 'two.sided')
t.test(aida2018.ActiveAgeL, aida2018.FailedAgeL, alternative = 'less')
t.test(aida2018.ActiveAgeL, aida2018.FailedAgeL, alternative = 'greater')

rm(aida2018.ActiveAgeG, aida2018.FailedAgeG, aida2018.ActiveAgeL, aida2018.FailedAgeL)
```

## 2.2 Size Distribution
***
```{r, fig.width=10, fig.height=3}
# density of Size between failed and active companies at year 2018
ggplot(data=aida2018, aes(x=Size, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +
  ggtitle("Density function of company size in 2018")
```
```{r}
# data for statistical tests, size distribution
aida2018.ActiveSize <- aida2018[aida2018$Status=='Active','Size']
aida2018.FailedSize <- aida2018[aida2018$Status=='Failed','Size']

wilcox.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'two.sided')
wilcox.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'less')
wilcox.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'greater')

t.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'two.sided')
t.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'less')
t.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'greater')

ks.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'two.sided')
ks.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'less')
ks.test(aida2018.ActiveSize, aida2018.FailedSize, alternative = 'greater')

rm(aida2018.ActiveSize, aida2018.FailedSize)
```

### 2.2.1 Size Distribution for specific company forms
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of size in 2018 for S.R.L. and S.P.A. companies
ggplot(data=aida2018[aida2018$`Legal form` == 'S.R.L.',], aes(x=`Size`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of size for S.R.L. companies in 2018")
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of size in 2018 for S.P.A. companies
ggplot(data=aida2018[aida2018$`Legal form` == 'S.P.A.',], aes(x=`Size`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of size for S.P.A. companies in 2018")
```
</div>
</div>

```{r}
# data for statistical tests, size distribution for specific legal form
aida2018.ActiveSizeSRL <- aida2018[aida2018$Status=='Active' & aida2018$`Legal form` == 'S.R.L.' ,'Size']
aida2018.FailedSizeSRL <- aida2018[aida2018$Status=='Failed' & aida2018$`Legal form` == 'S.R.L.' ,'Size']
aida2018.ActiveSizeSPA <- aida2018[aida2018$Status=='Active' & aida2018$`Legal form` == 'S.P.A.' ,'Size']
aida2018.FailedSizeSPA <- aida2018[aida2018$Status=='Failed' & aida2018$`Legal form` == 'S.P.A.' ,'Size']

t.test(aida2018.ActiveSizeSRL, aida2018.FailedSizeSRL, alternative = 'two.sided')
t.test(aida2018.ActiveSizeSRL, aida2018.FailedSizeSRL, alternative = 'less')
t.test(aida2018.ActiveSizeSRL, aida2018.FailedSizeSRL, alternative = 'greater')

t.test(aida2018.ActiveSizeSPA, aida2018.FailedSizeSPA, alternative = 'two.sided')
t.test(aida2018.ActiveSizeSPA, aida2018.FailedSizeSPA, alternative = 'less')
t.test(aida2018.ActiveSizeSPA, aida2018.FailedSizeSPA, alternative = 'greater')

rm(aida2018.ActiveSizeSRL, aida2018.FailedSizeSRL, aida2018.ActiveSizeSPA, aida2018.FailedSizeSPA)
```

### 2.2.2 Size Distribution for specific ATECO sectors
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of size in 2018 for ATECO G companies
ggplot(data=aida2018[aida2018$ATECO.Sector.Name == 'G',], aes(x=`Size`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of size for ATECO G companies in 2018")
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of size in 2018 for ATECO L companies
ggplot(data=aida2018[aida2018$ATECO.Sector.Name == 'L',], aes(x=`Size`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of size for ATECO L companies in 2018")
```
</div>
</div>

```{r}
# data for statistical tests, size distribution for specific ATECO sector
aida2018.ActiveSizeG <- aida2018[aida2018$Status=='Active' & aida2018$ATECO.Sector.Name == 'G' ,'Size']
aida2018.FailedSizeG <- aida2018[aida2018$Status=='Failed' & aida2018$ATECO.Sector.Name == 'G' ,'Size']
aida2018.ActiveSizeL <- aida2018[aida2018$Status=='Active' & aida2018$ATECO.Sector.Name == 'L' ,'Size']
aida2018.FailedSizeL <- aida2018[aida2018$Status=='Failed' & aida2018$ATECO.Sector.Name == 'L' ,'Size']

t.test(aida2018.ActiveSizeG, aida2018.FailedSizeG, alternative = 'two.sided')
t.test(aida2018.ActiveSizeG, aida2018.FailedSizeG, alternative = 'less')
t.test(aida2018.ActiveSizeG, aida2018.FailedSizeG, alternative = 'greater')

t.test(aida2018.ActiveSizeL, aida2018.FailedSizeL, alternative = 'two.sided')
t.test(aida2018.ActiveSizeL, aida2018.FailedSizeL, alternative = 'less')
t.test(aida2018.ActiveSizeL, aida2018.FailedSizeL, alternative = 'greater')


rm(aida2018.ActiveSizeG, aida2018.FailedSizeG, aida2018.ActiveSizeL, aida2018.FailedSizeL)
```

## 2.3 Liquidity Distribution
***
```{r, fig.width=10, fig.height=3}
# density of profit between failed and active companies at year 2018
ggplot(data=aida2018, aes(x=LiquidityRatio, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +
  ggtitle("Density function of company liquidity in 2018")
```
```{r}
# data for statistical tests, size distribution
aida2018.ActiveLiq <- aida2018[aida2018$Status=='Active','LiquidityRatio']
aida2018.FailedLiq <- aida2018[aida2018$Status=='Failed','LiquidityRatio']

wilcox.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'two.sided')
wilcox.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'less')
wilcox.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'greater')

t.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'two.sided')
t.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'less')
t.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'greater')

ks.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'two.sided')
ks.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'less')
ks.test(aida2018.ActiveLiq, aida2018.FailedLiq, alternative = 'greater')

rm(aida2018.ActiveLiq, aida2018.FailedLiq)
```
### 2.3.1 Liquidity Distribution for specific company forms
***
In order to select a company form that would provide us with a statistically significant difference, we decided to take a look at how _Legal form_ interacts with _Liquidity_.
By looking at the previous figure and the plots in section 1.3., we decided to focus on S.P.A. companies because they are on average the oldest, and also on S.R.L., being the most frequent.

<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of liquidity in 2018 for S.R.L. companies
ggplot(data=aida2018[aida2018$`Legal form` == 'S.R.L.',], aes(x=`LiquidityRatio`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of liquidity for S.R.L. companies in 2018")
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of liquidity in 2018 for S.A.S. companies
ggplot(data=aida2018[aida2018$`Legal form` == 'S.A.S.',], aes(x=`LiquidityRatio`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of liquidity for S.A.S. companies in 2018")
```
</div>
</div>
```{r}
# data for statistical tests, liquidity distribution for specific legal form
aida2018.ActiveLiquiditySRL <- aida2018[aida2018$Status=='Active' & aida2018$`Legal form` == 'S.R.L.' ,'LiquidityRatio']
aida2018.FailedLiquiditySRL <- aida2018[aida2018$Status=='Failed' & aida2018$`Legal form` == 'S.R.L.' ,'LiquidityRatio']
aida2018.ActiveLiquiditySAS <- aida2018[aida2018$Status=='Active' & aida2018$`Legal form` == 'S.A.S.' ,'LiquidityRatio']
aida2018.FailedLiquiditySAS <- aida2018[aida2018$Status=='Failed' & aida2018$`Legal form` == 'S.A.S..' ,'LiquidityRatio']

t.test(aida2018.ActiveLiquiditySRL, aida2018.FailedLiquiditySRL, alternative = 'two.sided')
t.test(aida2018.ActiveLiquiditySRL, aida2018.FailedLiquiditySRL, alternative = 'less')
t.test(aida2018.ActiveLiquiditySRL, aida2018.FailedLiquiditySRL, alternative = 'greater')

t.test(aida2018.ActiveLiquiditySAS, aida2018.FailedLiquiditySAS, alternative = 'two.sided')
t.test(aida2018.ActiveLiquiditySAS, aida2018.FailedLiquiditySAS, alternative = 'less')
t.test(aida2018.ActiveLiquiditySAS, aida2018.FailedLiquiditySAS, alternative = 'greater')

rm(aida2018.ActiveLiquiditySRL, aida2018.FailedLiquiditySRL, aida2018.ActiveLiquiditySAS, aida2018.FailedLiquiditySAS)
```

### 2.3.2 Other Distribution for specific ATECO sectors
***
As before with _Legal form_, we inspect the boxplots of _Liquidity_ and _ATECTO Sector Codes_ in search of interesting insights:
In a similar fashion, we picked the most frequent sector, being G, and the oldest on average, B, but with further inspection realized that B has a frequency of only 3001 records, representing less than 0.2% of the dataset, we therefore went with a more representative sector, L, with 205858 observations.

<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of liquidity in 2018 for ATECO J companies
ggplot(data=aida2018[aida2018$ATECO.Sector.Name == 'J',], aes(x=`LiquidityRatio`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of liquidity for ATECO J companies in 2018")
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
# density of liquidity in 2018 for ATECO L companies
ggplot(data=aida2018[aida2018$ATECO.Sector.Name == 'L',], aes(x=`LiquidityRatio`, fill=Status)) +
  geom_density(alpha=.5) +
  theme_light() +  
  ggtitle("Density function of liquidity for ATECO L companies in 2018")
```
</div>
</div>

```{r}
# data for statistical tests, liquidity distribution for specific ATECO sector
aida2018.ActiveLiquidityJ <- aida2018[aida2018$Status=='Active' & aida2018$ATECO.Sector.Name == 'J' ,'LiquidityRatio']
aida2018.FailedLiquidityJ <- aida2018[aida2018$Status=='Failed' & aida2018$ATECO.Sector.Name == 'J' ,'LiquidityRatio']
aida2018.ActiveLiquidityL <- aida2018[aida2018$Status=='Active' & aida2018$ATECO.Sector.Name == 'L' ,'LiquidityRatio']
aida2018.FailedLiquidityL <- aida2018[aida2018$Status=='Failed' & aida2018$ATECO.Sector.Name == 'L' ,'LiquidityRatio']

t.test(aida2018.ActiveLiquidityJ, aida2018.FailedLiquidityJ, alternative = 'two.sided')
t.test(aida2018.ActiveLiquidityJ, aida2018.FailedLiquidityJ, alternative = 'less')
t.test(aida2018.ActiveLiquidityJ, aida2018.FailedLiquidityJ, alternative = 'greater')

t.test(aida2018.ActiveLiquidityL, aida2018.FailedLiquidityL, alternative = 'two.sided')
t.test(aida2018.ActiveLiquidityL, aida2018.FailedLiquidityL, alternative = 'less')
t.test(aida2018.ActiveLiquidityL, aida2018.FailedLiquidityL, alternative = 'greater')

rm(aida2018.ActiveLiquidityJ, aida2018.FailedLiquidityJ, aida2018.ActiveLiquidityL, aida2018.FailedLiquidityL)
```


