---
title: "Statistics for Data Science Project 2021/2022 - Risk of Business Failure"
subtitle: "Question C"
output: 
  html_notebook:
    toc: true
    theme:
      bootswatch: cerulean 
---
By:  
Carla Lorena Trejo Silva\
Jordanos Feyissa Gemechu\
Bruno Javier Limon Avila\

# Data Preparation
***
```{r}
library(ggplot2)
library(dplyr)
```
```{r}
# cleaning the environment
rm(list=ls())
# loading the dataset
load(file="aida.RData")
# loading functions to be used
source("functions.R")
```
```{r}
# features added by using the functions in "functions.R"
aida <- getSize(aida)
aida <- getGeoArea(aida)
aida <- getStatus(aida)
aida <- getAge(aida)
aida <- getATECO(aida)
aida <- getLiquidity(aida)
# separating dataset filtering by year
aida.currYr <- getCurrYr(aida)
aida.yr1 <- getYr1(aida)
aida.yr2 <- getYr2(aida)
# focusing on a specific year
aida2017 <- aida.currYr[aida.currYr$`Last accounting closing date` == 2017,]
```
# 4.0 Question C
***
What is the probability of failures conditional to size/age/other of firms at a specific year?

- does it change for a specific company form (SPA, SRL, etc.) 
- do they change for a specific industry sector? (see ATECO sectors)
- does it change for a specific location? (eg., Tuscany, Lombardy, etc.)

## 4.1 Failure conditional to Age
***
```{r, fig.width=10, fig.height=3}
# we create a table containing the frequency of Failed/Active status for each age of the companies in 2017
aida2017.AgeStatus <- table(aida2017[,c('Age','Status')])
# conditional probability of failing knowing the age of companies
# P(Failed | Age)
Active <- aida2017.AgeStatus[,1]
Failed <- aida2017.AgeStatus[,2]
Pstatus <- (Failed / (Active + Failed))

# creating matrix with the proportion of failed companies with respect to each age available
aida2017.FailCondAge <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Age" = Pstatus)

head(aida2017.FailCondAge)
    
barplot(aida2017.FailCondAge[,3], main = "Conditional probability of failing in 2017 knowing the age of companies", xlab = 'Age', ylab = 'P(Failed | Age)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017.AgeStatus, Active, Failed, Pstatus, aida2017.FailCondAge)
```
### 4.1.1 Failure conditional to Age for specific company forms
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017SRL <- aida2017[aida2017$`Legal form` == 'S.R.L.',]  
aida2017.AgeStatusSRL <- table(aida2017SRL[,c('Age','Status')])

# P(Failed | Age)
Active <- aida2017.AgeStatusSRL[,1]
Failed <- aida2017.AgeStatusSRL[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondSRL <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Age" = Pstatus)

head(aida2017.FailCondSRL)

# Conditional probability of failing knowing the age of SRL companies
barplot(aida2017.FailCondSRL[,3], main = "Conditional probability of failing in 2017 knowing the age of SRL companies", xlab = 'Age', ylab = 'P(Failed | Age)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017SRL, aida2017.AgeStatusSRL, Active, Failed, Pstatus, aida2017.FailCondSRL)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017SPA <- aida2017[aida2017$`Legal form` == 'S.P.A.',]  
aida2017.AgeStatusSPA <- table(aida2017SPA[,c('Age','Status')])

# P(Failed | Age)
Active <- aida2017.AgeStatusSPA[,1]
Failed <- aida2017.AgeStatusSPA[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondSPA <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Age" = Pstatus)

head(aida2017.FailCondSPA)

# plot Conditional probability of failing knowing the age of SPA companies
barplot(aida2017.FailCondSPA[,3], main = "Conditional probability of failing in 2017 knowing the age of SPA companies", xlab = 'Age', ylab = 'P(Failed | Age)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017SPA, aida2017.AgeStatusSPA, Active, Failed, Pstatus, aida2017.FailCondSPA)
```
</div>
</div>
### 4.1.2 Failure conditional to Age for specific ATECO sectors
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017G <- aida2017[aida2017$ATECO.Sector.Name == 'G',]  
aida2017.AgeStatusG <- table(aida2017G[,c('Age','Status')])

# P(Failed | Age)
Active <- aida2017.AgeStatusG[,1]
Failed <- aida2017.AgeStatusG[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondG <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Age" = Pstatus)

head(aida2017.FailCondG)

# plot Conditional probability of failing knowing the age of ATECO G companies
barplot(aida2017.FailCondG[,3], main = "Conditional probability of failing in 2017 knowing the age of ATECO G companies", xlab = 'Age', ylab = 'P(Failed | Age)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017G, aida2017.AgeStatusG, Active, Failed, Pstatus, aida2017.FailCondG)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017L <- aida2017[aida2017$ATECO.Sector.Name == 'L',]  
aida2017.AgeStatusL <- table(aida2017L[,c('Age','Status')])

# P(Failed | Age)
Active <- aida2017.AgeStatusL[,1]
Failed <- aida2017.AgeStatusL[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondL <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Age" = Pstatus)

head(aida2017.FailCondL) 

# plot Conditional probability of failing knowing the age of ATECO L companies
barplot(aida2017.FailCondL[,3], main = "Conditional probability of failing in 2017 knowing the age of ATECO L companies", xlab = 'Age', ylab = 'P(Failed | Age)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017L, aida2017.AgeStatusL, Active, Failed, Pstatus, aida2017.FailCondL)
```
</div>
</div>
### 4.1.3 Failure conditional to Age for specific locations
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017Lazio <- aida2017[aida2017$`Registered office address - Region` == 'Lazio',]  
aida2017.AgeStatusLazio <- table(aida2017Lazio[,c('Age','Status')])

# P(Failed | Age)
Active <- aida2017.AgeStatusLazio[,1]
Failed <- aida2017.AgeStatusLazio[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLazio <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Age" = Pstatus)

head(aida2017.FailCondLazio)

# plot Conditional probability of failing knowing the age of Lazio companies
barplot(aida2017.FailCondLazio[,3], main = "Conditional probability of failing in 2017 knowing the age of Lazio companies", xlab = 'Age', ylab = 'P(Failed | Age)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017Lazio, aida2017.AgeStatusLazio, Active, Failed, Pstatus, aida2017.FailCondLazio)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017Emilia <- aida2017[aida2017$`Registered office address - Region` == 'Emilia-Romagna',]  
aida2017.AgeStatusEmilia <- table(aida2017Emilia[,c('Age','Status')])

# P(Failed | Age)
Active <- aida2017.AgeStatusEmilia[,1]
Failed <- aida2017.AgeStatusEmilia[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondEmilia <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Age" = Pstatus)

head(aida2017.FailCondEmilia)

# plot Conditional probability of failing knowing the age of Emilia-Romagna companies
barplot(aida2017.FailCondEmilia[,3], main = "Conditional probability of failing in 2017 knowing the age of Emilia-Romagna companies", xlab = 'Age', ylab = 'P(Failed | Age)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017Emilia, aida2017.AgeStatusEmilia, Active, Failed, Pstatus, aida2017.FailCondEmilia)
```
## 4.2 Failure conditional to Size
***
```{r, fig.width=10, fig.height=3}
# Using Friedman-Diaconis rule to calculate the bin-width, h=2×IQR×n^1/3, num.bins=(max−min)/h 
fd <- (2*IQR(aida2017$Size)) / (length(aida2017$Size)^(1/3))
num.bins <- as.integer((max(aida2017$Size) - min(aida2017$Size)) / fd)
aida2017$Size.Binned <- cut(x=aida2017$Size, breaks = num.bins)

aida2017.SizeStatus <- table(aida2017[,c('Size.Binned','Status')])

# P(Failed | Age)
Active <- aida2017.SizeStatus[,1]
Failed <- aida2017.SizeStatus[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondSize <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Size" = Pstatus)

head(aida2017.FailCondSize)

# Conditional probability of failing knowing the size of companies
barplot(aida2017.FailCondSize[,3], main = "Conditional probability of failing in 2017 knowing the size of companies", xlab = 'Size', ylab = 'P(Failed | Size)', col = "#2FA4E7", border ="#2FA4E7", space = .1)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(fd, num.bins, aida2017.SizeStatus, Active, Failed, Pstatus, aida2017.FailCondSize)
```
### 4.2.1 Failure conditional to Size for specific company forms
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017SRL <- aida2017[aida2017$`Legal form` == 'S.R.L.',]  
aida2017.SizeStatusSRL <- table(aida2017SRL[,c('Size.Binned','Status')])

# P(Failed | Size)
Active <- aida2017.SizeStatusSRL[,1]
Failed <- aida2017.SizeStatusSRL[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondSizeSRL <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Size" = Pstatus)

head(aida2017.FailCondSizeSRL)

# Conditional probability of failing knowing the size of SRL companies
barplot(aida2017.FailCondSizeSRL[,3], main = "Conditional probability of failing in 2017 knowing the size of SRL companies", xlab = 'Size', ylab = 'P(Failed | Size)', col = "#2FA4E7", border ="#2FA4E7", space = .1)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017SRL, aida2017.SizeStatusSRL, Active, Failed, Pstatus, aida2017.FailCondSizeSRL)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017SPA <- aida2017[aida2017$`Legal form` == 'S.P.A.',]  
aida2017.SizeStatusSPA <- table(aida2017SPA[,c('Size.Binned','Status')])

# P(Failed | Size)
Active <- aida2017.SizeStatusSPA[,1]
Failed <- aida2017.SizeStatusSPA[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondSizeSPA <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Size" = Pstatus)

head(aida2017.FailCondSizeSPA)

# plot Conditional probability of failing knowing the size of SPA companies
barplot(aida2017.FailCondSizeSPA[,3], main = "Conditional probability of failing in 2017 knowing the size of SPA companies", xlab = 'Size', ylab = 'P(Failed | Size)', col = "#2FA4E7", border ="#2FA4E7", space = .1)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017SPA, aida2017.SizeStatusSPA, Active, Failed, Pstatus, aida2017.FailCondSizeSPA)
```
</div>
</div>
### 4.2.2 Failure conditional to Size for specific ATECO sectors
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017G <- aida2017[aida2017$ATECO.Sector.Name == 'G',]  
aida2017.SizeStatusG <- table(aida2017G[,c('Size.Binned','Status')])

# P(Failed | Size)
Active <- aida2017.SizeStatusG[,1]
Failed <- aida2017.SizeStatusG[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondG <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Size" = Pstatus)

head(aida2017.FailCondG)

# plot Conditional probability of failing knowing the size of ATECO G companies
barplot(aida2017.FailCondG[,3], main = "Conditional probability of failing in 2017 knowing the size of ATECO G companies", xlab = 'Size', ylab = 'P(Failed | Size)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017G, aida2017.SizeStatusG, Active, Failed, Pstatus, aida2017.FailCondG)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017L <- aida2017[aida2017$ATECO.Sector.Name == 'L',]  
aida2017.SizeStatusL <- table(aida2017L[,c('Size.Binned','Status')])

# P(Failed | Size)
Active <- aida2017.SizeStatusL[,1]
Failed <- aida2017.SizeStatusL[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondL <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Size" = Pstatus)

head(aida2017.FailCondL) 

# plot Conditional probability of failing knowing the size of ATECO L companies
barplot(aida2017.FailCondL[,3], main = "Conditional probability of failing in 2017 knowing the size of ATECO L companies", xlab = 'Size', ylab = 'P(Failed | Size)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017L, aida2017.SizeStatusL, Active, Failed, Pstatus, aida2017.FailCondL)
```
</div>
</div>

### 4.2.3 Failure conditional to Size for specific locations
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017Lazio <- aida2017[aida2017$`Registered office address - Region` == 'Lazio',]  
aida2017.SizeStatusLazio <- table(aida2017Lazio[,c('Size.Binned','Status')])

# P(Failed | Size)
Active <- aida2017.SizeStatusLazio[,1]
Failed <- aida2017.SizeStatusLazio[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLazio <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Size" = Pstatus)

head(aida2017.FailCondLazio)

# plot Conditional probability of failing knowing the size of Lazio companies
barplot(aida2017.FailCondLazio[,3], main = "Conditional probability of failing in 2017 knowing the size of Lazio companies", xlab = 'Size', ylab = 'P(Failed | Size)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017Lazio, aida2017.SizeStatusLazio, Active, Failed, Pstatus, aida2017.FailCondLazio)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017Emilia <- aida2017[aida2017$`Registered office address - Region` == 'Emilia-Romagna',]  
aida2017.SizeStatusEmilia <- table(aida2017Emilia[,c('Size.Binned','Status')])

# P(Failed | Size)
Active <- aida2017.SizeStatusEmilia[,1]
Failed <- aida2017.SizeStatusEmilia[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondEmilia <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|Size" = Pstatus)

head(aida2017.FailCondEmilia)

# plot Conditional probability of failing knowing the size of Emilia-Romagna companies
barplot(aida2017.FailCondEmilia[,3], main = "Conditional probability of failing in 2017 knowing the size of Emilia-Romagna companies", xlab = 'Size', ylab = 'P(Failed | Size)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017Emilia, aida2017.SizeStatusEmilia, Active, Failed, Pstatus, aida2017.FailCondEmilia)
```

## 4.3 Failure conditional to Liquidity
***
```{r, fig.width=10, fig.height=3}
# we create a table containing the frequency of Failed/Active status for each liquidity ratio of the companies in 2017

fd <- (2*IQR(aida2017$LiquidityRatio)) / (length(aida2017$LiquidityRatio)^(1/3))
num.bins <- as.integer((max(aida2017$LiquidityRatio) - min(aida2017$LiquidityRatio)) / fd)
aida2017$LiquidityRatio.binned <- cut(x=aida2017$LiquidityRatio, breaks = num.bins)

aida2017.LiquidityStatus <- table(aida2017[,c('LiquidityRatio.binned','Status')])

# conditional probability of failing knowing the age of companies
# P(Failed | Age)
Active <- aida2017.LiquidityStatus[,1]
Failed <- aida2017.LiquidityStatus[,2]
Pstatus <- (Failed / (Active + Failed))

# creating matrix with the proportion of failed companies with respect to each age available
aida2017.FailCondLiq <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|LiquidityRatio" = Pstatus)

head(aida2017.FailCondLiq)

barplot(aida2017.FailCondLiq[,3], main = "Conditional probability of failing in 2017 knowing the liquidity ratio of companies", xlab = 'LiquidityRatio', ylab = 'P(Failed | LiquidityRatio)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017.LiquidityStatus, Active, Failed, Pstatus, aida2017.FailCondLiq)
```
### 4.3.1 Failure conditional to Other for specific company forms
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017SRL <- aida2017[aida2017$`Legal form` == 'S.R.L.',]  
aida2017.LiquidityStatusSRL <- table(aida2017SRL[,c('LiquidityRatio.binned','Status')])

# P(Failed | LiquidityRatio)
Active <- aida2017.LiquidityStatusSRL[,1]
Failed <- aida2017.LiquidityStatusSRL[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLiqSRL <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|LiquidityRatio" = Pstatus)

head(aida2017.FailCondLiqSRL)

# Conditional probability of failing knowing the liquidity ratio of SRL companies
barplot(aida2017.FailCondLiqSRL[,3], main = "Conditional probability of failing in 2017 knowing the liquidity ratio of SRL companies", xlab = 'LiquidityRatio', ylab = 'P(Failed | LiquidityRatio)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017SRL, aida2017.LiquidityStatusSRL, Active, Failed, Pstatus, aida2017.FailCondLiqSRL)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017SAS <- aida2017[aida2017$`Legal form` == 'S.A.S.',]  
aida2017.LiquidityStatusSAS <- table(aida2017SAS[,c('LiquidityRatio.binned','Status')])

# P(Failed | LiquidityRatio)
Active <- aida2017.LiquidityStatusSAS[,1]
Failed <- aida2017.LiquidityStatusSAS[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLiqSAS <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|LiquidityRatio" = Pstatus)

head(aida2017.FailCondLiqSAS)

# plot Conditional probability of failing knowing the liquidity ratio of SAS companies
barplot(aida2017.FailCondLiqSAS[,3], main = "Conditional probability of failing in 2017 knowing the liquidity ratio of SAS companies", xlab = 'LiquidityRatio', ylab = 'P(Failed | LiquidityRatio)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017SAS, aida2017.LiquidityStatusSAS, Active, Failed, Pstatus, aida2017.FailCondLiqSAS)
```
</div>
</div>
### 4.3.2 Failure conditional to Other for specific ATECO sectors
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017J <- aida2017[aida2017$ATECO.Sector.Name == 'J',]  
aida2017.LiquidityStatusJ <- table(aida2017J[,c('LiquidityRatio.binned','Status')])

# P(Failed | LiquidityRatio)
Active <- aida2017.LiquidityStatusJ[,1]
Failed <- aida2017.LiquidityStatusJ[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLiqJ <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|LiquidityRatio" = Pstatus)

head(aida2017.FailCondLiqJ)

# plot Conditional probability of failing knowing the liquidity ratio of ATECO J companies
barplot(aida2017.FailCondLiqJ[,3], main = "Conditional probability of failing in 2017 knowing the liquidity ratio of ATECO J companies", xlab = 'LiquidityRatio', ylab = 'P(Failed | LiquidityRatio)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017J, aida2017.LiquidityStatusJ, Active, Failed, Pstatus, aida2017.FailCondLiqJ)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017L <- aida2017[aida2017$ATECO.Sector.Name == 'L',]  
aida2017.LiquidityStatusL <- table(aida2017L[,c('LiquidityRatio.binned','Status')])

# P(Failed | LiquidityRatio)
Active <- aida2017.LiquidityStatusL[,1]
Failed <- aida2017.LiquidityStatusL[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLiqL <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|LiquidityRatio" = Pstatus)

head(aida2017.FailCondLiqL) 

# plot Conditional probability of failing knowing the liquidity ratio of ATECO L companies
barplot(aida2017.FailCondLiqL[,3], main = "Conditional probability of failing in 2017 knowing the liquidity ratio of ATECO L companies", xlab = 'LiquidityRatio', ylab = 'P(Failed | LiquidityRatio)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017L, aida2017.LiquidityStatusL, Active, Failed, Pstatus, aida2017.FailCondLiqL)
```
</div>
</div>
### 4.3.3 Failure conditional to Other for specific locations
***
<div class = "row">
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017Lombardia <- aida2017[aida2017$`Registered office address - Region` == 'Lombardia',]  
aida2017.LiquidityStatusLombardia <- table(aida2017Lombardia[,c('LiquidityRatio.binned','Status')])

# P(Failed | LiquidityRatio)
Active <- aida2017.LiquidityStatusLombardia[,1]
Failed <- aida2017.LiquidityStatusLombardia[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLiqLombardia <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|LiquidityRatio" = Pstatus)

head(aida2017.FailCondLiqLombardia)

# plot Conditional probability of failing knowing the liquidity ratio of Lombardia companies
barplot(aida2017.FailCondLiqLombardia[,3], main = "Conditional probability of failing in 2017 knowing the liquidity ratio of lombardia companies", xlab = 'LiquidityRatio', ylab = 'P(Failed | LiquidityRatio)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017Lombardia, aida2017.LiquidityStatusLombardia, Active, Failed, Pstatus, aida2017.FailCondLiqLombardia)
```
</div>
<div class = "col-md-6"> 
```{r, fig.width=8, fig.height=5}
aida2017Emilia <- aida2017[aida2017$`Registered office address - Region` == 'Emilia-Romagna',]  
aida2017.LiquidityStatusEmilia <- table(aida2017Emilia[,c('LiquidityRatio.binned','Status')])

# P(Failed | LiquidityRatio)
Active <- aida2017.LiquidityStatusEmilia[,1]
Failed <- aida2017.LiquidityStatusEmilia[,2]
Pstatus <- (Failed / (Active + Failed))

aida2017.FailCondLiqEmilia <- cbind(
  Active = Active,
  Failed = Failed,
  "%Failed|LiquidityRatio" = Pstatus)

head(aida2017.FailCondLiqEmilia)

# plot Conditional probability of failing knowing the Liquidity ratio of Emilia-Romagna companies
barplot(aida2017.FailCondLiqEmilia[,3], main = "Conditional probability of failing in 2017 knowing the liquidity ratio of Emilia-Romagna companies", xlab = 'LiquidityRatio', ylab = 'P(Failed | LiquidityRatio)', col = "#2FA4E7", border ="#2FA4E7", space = .3)
abline(h = seq(.2,1.0,.2), lty = "dashed", col = "#a8a8a8")

rm(aida2017Emilia, aida2017.LiquidityStatusEmilia, Active, Failed, Pstatus, aida2017.FailCondLiqEmilia)
```
